?? Mixture Model

### 2016-10-10 docs/ver1.tex
sync

\title
    {{Sparse Mixture Model (with jk-means a special case)}}

@@

\section{Sparse Mixture Model}

@@

On a separable metrics space $\{\mathcal{X},\mathcal{F}\}$, we assume each data $y_i$ has the following probabilty density as the likelihood:

\begin{equation}
\begin{aligned}
& [ y_i ] = \sum_{k=1}^{\kappa} w_{k,i} \delta_{\theta_{k}}(y_i) \\
& w_{k,i} = \frac{ u_{k,i} v_{k} } { \sum_{k=1}^{\kappa}  u_{k,i} v_{k} }\\
& u_{k,i} \in \{0,1\}
\end{aligned}
\label{marginal_lik}
\end{equation}
where $\delta_{\theta_{k}}(y_i)$ is a probabilty density corresponds to a component distribution with parameter $\theta_{k}$, and $w_{k,i}$ is the component weight that varies by index $i$ and $\sum_{k=1}^{\kappa} w_{k,i} =1$. The weight varying is due to the randomness in $u_{k,i}$. Due to the $0$'s $u_{k,i}$ introduces, this induces sparsity in the membership probabilty $w_{k,i}$. Therefore, we refer this as the sparse mixture model.

@@

\subsubsection{JK-Means}

With the above general framework, there is a special case $\{ u_{1,i},u_{2,i},\ldots u_{\kappa,i}\} \sim \text{ J out of K draws}$ and $\nu_k = 1/\kappa$. We refer this as JK-Means as when $J=1$, this reduces to standard K-means method. The estimation procedure is the same as above except step \ref{flex_w_step} is skipped.

>>>>

\title
    {?? Mixture Model}

@@

\section{Introduction}

hard clustering:
several overly strong assumptions in k-means

soft clustering:
large variance induced by way too many non-zeros in the probability simplex.

variance-bias tradeoff?
reducing variability on the weight

\section{?? Mixture Model}

@@

On a separable metrics space $\{\mathcal{X},\mathcal{F}\}$, we assume each data $y_i$ has the following probability density as the likelihood:

\begin{equation}
\begin{aligned}
& \pi(y_i) \sim G(\theta_i) \\
& \pi(\theta_i) = \sum_{k=1}^{\kappa} w_{k,i} \delta_{\theta_{k}}(\theta_i) \\
& w_{k,i} = \frac{ u_{k,i} v_{k} } { \sum_{k=1}^{\kappa}  u_{k,i} v_{k} }\\
& u_{k,i} \in \{0,1\}
\end{aligned}
\label{marginal_lik}
\end{equation}
where $\delta_{\theta_{k}}(y_i)$ is a probabilty density corresponds to a component distribution with parameter $\theta_{k}$, and $w_{k,i}$ is the component weight that varies by index $i$ and $\sum_{k=1}^{\kappa} w_{k,i} =1$. The weight varying is due to the randomness in $u_{k,i}$. Due to the $0$'s $u_{k,i}$ introduces, this induces sparsity in the membership probabilty $w_{k,i}$.

@@

\section{Theory}

variance reduction in the weight parameter

\section{Simulation}

large K with small J in 1d

high p setting

\section{Application}
\section{Discussion}
